---
title: "assignment_3"
author: "Jessie Lilly"
date: "March 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Tidyverse

```{r}
library(tidyverse)
```

## 1. Create your own Poisson Distibution

## Detect whether the mean squirrel density differs between a 1km transect taken from 5 farmers field adjacent from the dikes in Wolfville, or a 5 1km forested transects sampled just north from Kentville. 

## First we need an indicator for site use. 

```{r}
n.sites <- 5 ## 5 samples taken at each site.

x <- gl(n=2,k=n.sites, labels = c("field","forest")) ## Indicator variable for sites.

n <- 2*n.sites ##total number of sites.
```


## The mean squirrel density in the farmers fields is 3, and the mean squirrel denity ## forrested areas is 12. Then alpha= log(3)= 0.47712, and log(12) =alpha + beta. 
## Beta= log(12)-log(3)= 
## 0.60206
## Therefore, the expected density lambdai is given by:
```{r}
lambda <- exp(0.47712+0.60206*(as.numeric(x)-1)) # x has levels 1 and 2 not,0 and 1
```

## Add noise that comes from a Poisson distribution and inspect the squirrel counts generated. 

```{r}
C <- rpois(n=n, lambda=lambda) ## add poisson noise
```

## Fit the poisson t test

```{r}
poisson.t.test <- glm(C~x,family=poisson) # Fit the model
summary(poisson.t.test) # T test

```


2. 

## Create a boxplot to compare squirrel tail length from the forest. 

```{r}
ngroups <- 5 ## number of groups of squirrels sampled in a forest near wolfville. 
nsamples<- 25 ## 25 squirrels were sampled in each transect. 
pop.means <- c(5,10,20,15,8)  ## mean tail length
resid.sd <- 3 ## the residuals. 

n <- ngroups * nsamples ## total number of data poinsts. 

eps <- rnorm(n,0,resid.sd) ## residuals 

x<- rep(pop.means,rep(nsample,ngroups)) ## Indicator for the population
means <- rep(pop.means,rep(nsample,ngroups))

X <- as.matrix (model.matrix(~as.factor(x)-1)) ## design matrix; no intercept! 

y<- as.numeric(X %*% as.matrix(pop.means)+eps)

squirrel.df <- data.frame(population=as.factor(x),tl=y)


```

## Create a boxplot of taillength versus sample group. 

```{r}
p <- ggplot(data=squirrel.df,aes(population,tl))

p+geom_boxplot()
```

## I am interested in whether there is a difference in the abundance of polychaete worms in Atlantic Sturgeon stomachs based on where they are captured in Minas Basin (Kingsport Beach, Blomidon Beach, and PorterWeir), and also whether total length(TL) effects this abundance. 

## log(lambda)= alpha(king)+ B1*X1(Blom)+ B2*X2(Por)+B3*X(TL)+B4*X(TL)*X(Blom)+B4XTL*XPor

## Data generation

```{r}
n.groups <- 3
n.sample<- 100
n<- n.groups*n.sample

```

## Create a population indicator
```{r}
x <- rep(1:n.groups, rep(n.sample, n.groups)) ## population indicator

pop<- factor(x,labels= c("Kingsport","Blomidon","Porter"))

length <- runif(n,25,150) ## total length

length <- length-mean(length) ## center by subtracting the mean 
```

## Design a matrix - an interaction between length and population 
## I am not sure what to choose for my beta.vec numbers. 

```{r}
Xmat <- model.matrix(~pop *length)

beta.vec <- c(4,1,2,6,2,5)
```

## Assemble into a poisson model. 
## Build the design of the matrix as an interactive combination of length and population.

```{r}
lin.pred <- Xmat[,] %*% beta.vec
lambda <- exp(lin.pred) ## poisson mean
C <- rpois (n=n,lambda=lambda) ## poisson noise
```

## Now assess the model. 
## I am not sure what C~pop does? 
```{r}
m1 <- glm(C~pop*length,poisson)
summary(m1)
```
## Test model 
```{r}
par(mfrow=c(2,2))
plot(m1)
```


## Binomial Ancova

## Are Female Atlantic Sturgeon more likely to enter Minas Basin during May then male Atlantic Sturgeon. 

```{r}
N<- 50 #total number of Atlantic Sturgeon sampled in May 2015
p.fem <- 20/50 # Success probability of a female
p.mal <- 30/50 # Success probability of a male 
```

## Add Binomial noise 

```{r}
C.fem <- rbinom(1,50,prob=p.fem)  
C.mal <- rbinom (1,50,prob=p.mal)

C<- c(C.fem,C.mal)
sex <- factor(c(0,1),labels=c("Female","Male"))
```

## Binomial t-test in R suggets a significant difference in the percieved abundance of Male and female Atlantic Sturgeon entering Minas Basin during May. 

```{r}
summary(glm(cbind(C,N-C)~sex,family=binomial))


```

## What is the proportion of Atlantic Sturgeon detected at 3 recievers in Minas Basin when water temperatures are below 10 degrees celcius. 

```{r}
n.groups <- 3
n.sample <- 20
n <- n.groups*n.sample
```

```{r}
x <- rep(1:n.groups,rep(n.sample,n.groups)) ## indicator for population
pop <- factor(x,labels=c("Kingsport","Blomidon","Porter"))
```

## Construct a continous temperature index: 0 denotes sites less than 10 degrees celcius, and 1 is greater than 10 degrees celcius. 

```{r}
temperature.Kingsport <- sort(runif(n.sample,0,1))
temperature.Blomidon <- sort(runif(n.sample,0,1))
temperature.Porter <- sort(runif(n.sample,0,1))

temperature <- c(temperature.Blomidon,temperature.Kingsport,temperature.Porter)
```

## Also need the number of Atlantic Sturgeon examined in each population Ni. 

```{r}
N <- round(runif(n,20,50)) # get discrete uniform values
```

## Build the design matrix. 

```{r}
Xmat <- model.matrix(~pop*temperature)
print(Xmat,dig=2)
```
## Choose parameters 

```{r}
beta.vec <- c(5,1,3,7,3,4)
```

## Value of lin predictor matrix multiplication

```{r}
lin.pred <- Xmat[,] %*% beta.vec
exp.p <- exp(lin.pred)/(1+exp(lin.pred)) ## expected proportion
C<- rbinom(n=n,size=N,prob=exp.p)

```

## Expect what we created

```{r}
hist(C)
```

## Analyze

```{r}
m1 <- glm(cbind(C,N-C)~pop*temperature,binomial)
summary(m1)

```
## Check model 

```{r}
par(mfrow=c(2,2))
plot(m1)
```

