---
title: "Practice"
author: "Jessie Lilly"
date: "March 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load tidyverse. 

```{r}
library(tidyverse)
```



## Generate a function that will generate, for a range of each of 'magnitude of B1', 'sample size', and 'error', a measure of the quality of the parameter estimate. 

## 1 A) Create a function that will generate random data with a parameter of 5.
```{r}
gen.mod <- function(n=100, b0=2, b1=3, sd.err=1){predictor<-runif(n)-0.5
response <- b0+b1*predictor+rnorm(n, mean= 0,sd= sd.err)
return(data.frame(response = response, predictor = predictor))}
```

## Use the data from gen.mod to generate parameter estimates for 3 different B1 values.

```{r}
n.times <- 100
n <- c(10,15,20)
b1 <- c(0.2,0.5,0.8,1)
sd.err <- c(0.5,1,1.5,2)

est.df <- matrix(nrow=n.times,ncol=3,NA)


for (i in 1:n.times) { m1 <- lm(response ~ predictor, data=gen.mod (n=10, b0=2, b1= 0.2, sd.err= 1))
est.df[i,1] <- summary(m1)$coefficients["predictor","t value"]
m1 <- lm(response ~ predictor, data=gen.mod (n=15,b0=2, b1=0.5, sd.err=1))
est.df[i,2] <- summary(m1)$coefficients["predictor","t value"]
m1 <- lm(response ~ predictor, data=gen.mod(n=20,b0=4, b1=0.8, sd.err=1.5))
est.df[i,3] <- summary(m1)$coefficients["predictor","t value"]}

est.df <- data.frame(est.df)




```


## Retrieve a summary of the predictor variables 

```{r}
summary(m1)$coefficients["predictor", ]
```

## 3.  Graph the results from question 1. 
## First create a df that is sorted by each of the 3  fitted lines. 
## Then group each estimate by its trial number, and find the mean estimate (t-value) in order to determine visually which line has the best estimate value. 
## I don't understand this step. 

```{r}
est.df <- gather(est.df,value="est",key="trial")
est.df$trial <- factor(est.df$trial)

est.sum.df <- group_by(est.df,trial) %>% summarize(mn.est=mean(est))

p <- ggplot(aes(est,group=trial, col=trial), data=est.df)
p+geom_density()+geom_vline(data=est.sum.df,aes(xintercept=mn.est,col=trial))
```


## The function I would like to use but can't get to work. 
## I am trying to create 3 loops for each value of n,b1, sd.err and graph three seperate groups. However, I can't get 3 seperate groups and 3 seperate lines to graph. 

```{r}
n.times <- 100
n <- c(10,15,20,25)
b1 <- c(0.2,0.5,0.8,1)
sd.err <- c(0.5,1,1.5,2)

## pdt -- you actually want an empty data frame
est.df<- NULL ## an empty vector

## pdt: in here, you need to think a bit more about what you want est.df
## to look like. You are varying several different inputs into the 
## model, and so you want to track those somehow ... 

for(i in 1:4) {
  a <- n[i]
  for(k in 1:4) {
    b <- b1[k]
    for(z in 1:4) { c <- sd.err[z]
      for(j in 1:100){
           m1 <- lm(response ~ predictor, data=gen.mod(n[i],b0=1,b1[k],sd.err[z]))
           est.df[j,4]<-summary(m1)$coefficients["predictor","Estimate"]}}}}

est.df <- data.frame(est.df)

##split est.df into a data frame in long format

est.df <- gather(est.df,value="est",key="trial")

est.df$trial <- factor(est.df$trial)

est.sum.df <- group_by(est.df,trial) %>% summarize(mn.est = mean(est))

p<- ggplot(aes(est,group=trial,col=trial), data=est.df)

p+geom_density()+geom_vline(data=est.sum.df,aes(xintercept=mn.est,col=trial))





```

## Plot est.df into long format and group by individual trials. 

```{r}
est.df <- gather(est.df,value="est",key="trial")
est.df$trial <- factor(est.df$trial)

est.sum.df <- group_by(est.df,trial) %>% summarize(mn.est=mean(est))

p <- ggplot(aes(est,group=trial,col=trial),data=est.df)
p+geom_density()+geom_vline(data=est.sum.df,aes(xintercept=mn.est,col=trial))
```

## Do the same thing as above, but use a single parameter estimate of B1=0 (e.g. No effect). Set B0=0. Use a sample size of 100. Instead of using the t value as your quality estimate, have the function output the 'p value'. 

##What does exapnd.grid do?


```{r}

gen.df2 <- function(n=100,b0=0,b1=0,sd.err=1){
  predictor <- runif(n)-0.5
  response <- b0+b1 * predictor+rnorm(n,mean=0,sd=sd.err)
}



n.times <- 100
n <- c(10,15,20,25)
b1 <- c(0)
sd.err <- c(0.5,1,1.5,2)

test.df2 <- expand.grid(n.times=n.times,n=n,b1=b1,sd.err=sd.err)

for(i in 1:length(test.df$n.times)){
  tmp.df <- gen.df(n=test.df$n[i],b0=0,b1=test.df2$b1[i],sd.err=test.df2$sd.err[i])
  temp.lm2<- lm(response~predictor,data=tempdf2)
  test.df2$pval[i] <- summary(tmp.lm2)$coefficients["predictor","Pr(>|t|"]
}





```
## 4.a. For a given sample size and error,what does the distribution of the p-value look like?
```{r}
p2<- ggplot(data=test.df2,aes(pval,group=n,col=n))
p2 + geom_density()+facet_grid(~sd.err)

```
## 4.b What proportion of p values are <=0.05?
```{r}
pvalues <- which(test.df2$pval <=0.05)
tabulate(pvalues)
```
```{r}

```

